---
title: "Sentiment Analysis"
author: "Barrientos, Delfin, Infiesto"
date: "2024-11-28"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
library(dplyr)
library(ggplot2)
library(tidyr)
library(stringr)
library(syuzhet)

tweetsDF <- read_excel("C:/PROJ/tweetsDF.xlsx")


View(tweetsDF)

tweetsDF <- tweetsDF %>% 
  rename(
    screen_name = screenName,
    tweet = text,
    created_at = created,
    source = statusSource,
    rounded_time = Created_At_Round,
    tweet_source = tweetSource
  )

  tweetsDF <- tweetsDF %>%
    filter(!is.na(tweet), !is.na(created_at))
  
  tweetsDF$created_at <- as.POSIXct(tweetsDF$created_at, format = "%Y-%m-%d %H:%M:%S")

  str(tweetsDF)
  
  
tweets_trend <- tweetsDF %>%
  mutate(date = as.Date(created_at)) %>%
  group_by(date) %>%
  summarise(tweet_count = n())

# Plot the trend
ggplot(tweets_trend, aes(x = date, y = tweet_count)) +
  geom_line(color = "red", linewidth = 1) +
  labs(
    title = "Trend of Tweets Over Time",
    x = "Date",
    y = "Number of Tweets"
  ) +
  theme_minimal()

```
The graph titled "Trend of Tweets Over Time" shows how many tweets were posted each day over a certain time period. The dates are on the x-axis, and the number of tweets is on the y-axis. The red line connects the daily tweet counts, making it easy to see when there were more tweets or fewer tweets. Some days have a lot more tweets, which could mean something important happened, while other days have fewer tweets. This graph helps us see patterns in how people were posting tweets over time.


